Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-02 causal-bandit/icml-2015/introduction.tex
More tweaks

One obvious approach would be to cast the above example as a stochastic multi-armed bandit problem (\eg, the six possible farming interventions is an arm and the crop yield is the reward) and apply an algorithm such as UCB~\cite{Auer1995} with well understood regret guarantees.
However, as we show in \S\ref{sec:simple-regret}, this approach ignores the extra information available in the non-intervened variables and subsequently yields a worst-case regret after $T$ round of $\bigomega{\sqrt{NT}}$ with a sub-optimal dependence on $N$, the number of possible interventions.

Our framework also bears a superficial similarity to contextual bandit problems \cite{Langford2008,Agarwal2014} since the extra observations on non-intervened variables might be viewed as context for selecting an intervention. However, a crucial difference is that in our model the extra observations are only revealed \emph{after} selecting an intevention and cannot be used as context.

There has been a significant amount of recent work which proposes alternative modes of feedback within the bandit setting \cite{TODO} as well as results for partial monitoring which, at first glance, may appear applicable. Indeed, we show in Section~\ref{}, that it is possible to applying these existing results to our problem, however the resulting regret is $\bigo{\sqrt{NT}}$, again with a sub-optimal dependence on $N$.

@@

We take a first step towards unifying these approaches by considering a variant of the stochastic multi-armed bandit problem where we have prior knowledge of the causal structure governing the available actions.

\todom{Summarise results \& give intuition for algorithm}

>>>>

As alluded to above, causal bandit problems with $N$ possible interventions can be treated as a classical $N$-armed bandit problem by simply ignoring the causal model and extra observations that are revealed each round.
In the farming example, the farmer could treat the six possible interventions are arms, ignore the observations of the non-intervened variables, and apply an algorithm such as UCB~\cite{Auer1995} with well understood regret guarantees.
However, as we show in \S\ref{sec:simple-regret}, this approach ignores the extra information available in the non-intervened variables and subsequently yields sub-optimal performance.

Bandit problems with side information are commonly referred to as ``contextual bandits'' and have been well studied in recent years~\cite{Langford2008,Agarwal2014}.
Our framework bears a superficial similarity to contextual bandit problems since the extra observations on non-intervened variables might be viewed as context for selecting an intervention. 
However, a crucial difference is that in our model the extra observations are only revealed \emph{after} selecting an intervention and cannot be used as context.
We discuss the relationship between causal and contextual bandits further in \S\ref{sec:defs} and leave their combination as future work.

There has been a significant amount of recent work which proposes alternative modes of feedback within the bandit setting \citep{Alon2015} which, at first glance, may appear applicable. Indeed, we show in \S~\ref{sec:discussion}, that it is possible to applying these existing results to our problem, however the resulting regret is $\bigo{\sqrt{NT}}$, again with a sub-optimal dependence on $N$.

@@

% We take a first step towards unifying these approaches by considering a variant of the stochastic multi-armed bandit problem where we have prior knowledge of the causal structure governing the available actions.
